### 2015-02-08 docs/report/code_sharing.tex
Completed code_sharing.tex

That is an expected error as explained in section 9.5.3 of the HTML standard \cite{html-whatwg}, the value being sent must support the structured clone algorithm and a Function does not meet that requirement as explained in section 2.7.5 of that same standard. It could be assumed that this is because of the challenges of serializing function closures \cite{cloud-haskell} \cite{distributed-scheme}.

@@

These were the results:
\img{Comparing string encoding/decoding approaches}{../../spikes/2.2.1/test-syncEncodingAPI/encodingAPI}{fig:string-encode-decode}

@@

>>>>

That is an expected error as explained in section 9.5.3 of the HTML standard \cite{html-whatwg}, the value being sent must support the structured clone algorithm and a Function does not meet that requirement as explained in section 2.7.5 of that same standard. It could be assumed that this is because of the challenges of serializing function closures\cite{cloud-haskell}\cite{distributed-scheme}.

@@

The results for it are displayed in Figure~\ref{fig:string-encode-decode}.
\img{Comparing string encoding/decoding approaches}{../../spikes/2.2.1/test-syncEncodingAPI/encodingAPI}{fig:string-encode-decode}

@@

Additionally, in most scenarios code would have to be sent along with a \ttarray{} so it would also be interesting to see if the transfer time was affected by this fact.

\subsubsection{\tstring{} serialization and tranfer benchmarks}
We created a benchmark using two functions of different length to see if the function's length affected the serialization and transfer time. We measured three approaches to transfer the string:
\begin{enumerate}
  \item Encoding the \tstring{} into a \tabuffer{} and sending it as a \code{Tranferable} and decoding it on the Web Worker.
  \item Sending the string directly
  \item Using a \code{Blob} to store the stream and retrieving that in the Worker.
\end{enumerate}

The benchmark with the short function was the following one:
\bmcode{http://jsperf.com/pjs-serialization/2}{../../spikes/2.2.1/test-howToSendCode/shortSerialization.js}

The results for it are displayed in Figure~\ref{fig:short-serialization}.
\img{Comparing string encoding/decoding approaches}{../../spikes/2.2.1/test-howToSendCode/shortSerialization}{fig:short-serialization}

The benchmark with the long function was the following one:
\bmcode{http://jsperf.com/pjs-serialization-long}{../../spikes/2.2.1/test-howToSendCode/longSerialization.js}

The results for it are displayed in Figure~\ref{fig:long-serialization}.
\img{Comparing string encoding/decoding approaches}{../../spikes/2.2.1/test-howToSendCode/longSerialization}{fig:long-serialization}

\subsubsection{\tstring{} and \ttarray{} serialization and tranfer benchmarks}
We created a benchmark that tranfers a \ttarray{} and \tstring{} back and forth between the main thread an a worker to understand if transferring additional objects affected the transfer time when comparing it with just tranferring a \tstring{}.

The benchmark's code is the following one:
\bmcode{http://jsperf.com/pjs-encoding}{../../spikes/2.2.1/test-howToSendCodeWithData/encoding.js}

The results for it are displayed in Figure~\ref{fig:code-with-data}.
\img{Comparing string encoding/decoding approaches}{../../spikes/2.2.1/test-howToSendCodeWithData/encoding}{fig:code-with-data}

\subsubsection{Conclusion}
As the benchmarks show, the fastest way to tranfer the \tstring{} between the UI thread and workers is by directly sending it.
